Mechanized Reasoning about a Capability Machine

### 2019-10-18 prisc-2020/paper.tex
pass over sec 1

In summary, we present Iris formalizations of 
\begin{itemize}
  \item a program logic for reasoning about capability machine programs.
  \item the logical relation from \cite{skorstengaardESOP18}, 
    which captures capability safety and which can be used to reason about examples
    that rely on WBCF and LSE.
\end{itemize}
Most of the technical development is mechanized in Coq using the Coq implementation of Iris (the remaining work consists of a few missing details). Currently the mechanization consists of 5.8k lines of spec and 15k lines of proof as reported by \textsf{coqwc}. Its substantial size can be slightly improved by some clever use of tactics, however such a mechanization will always be large, due to the low level nature of a machine: we want to consider every possible case of an instruction, both the fails and the successes.
\todo{Alix: I would say it's more due to the nature of a capability machine with dynamic checks and the multiple ways they can fail}

>>>>

In summary, we present Iris formalizations of 
\begin{itemize}
  \item a program logic for reasoning about capability machine programs.
  \item the logical relation from \cite{skorstengaardESOP18}, 
    which captures capability safety and which can be used to reason about examples
    that rely on WBCF and LSE.
\end{itemize}
Currently, almost all of the technical development is mechanized in Coq using the Coq implementation of Iris.
The mechanization presently consists of 5.8K lines of spec and 15K lines of proof as reported by \textsf{coqwc}.
Its substantial size can probably be reduced by better use of tactics. However, such a mechanization will always be non-trivial due to the nature of the capability machine with dynamic checks
and multiple ways in which instructions can fail.
